Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-10-25 paper/main.tex
cha cha cha changes.....

We then hand-created 39 multiple-choice questions: 15 about the conceptual
content of \textit{Four Fundamental Forces} (i.e., Lecture~1), 15 about the
conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). To help broaden the
set of lecture-specific questions, our team worked through each lecture in
small segments to identify what each segment was ``about'' conceptually, and
then write a question about that concept. The general physics questions were
drawn our team's prior coursework and areas of interest, along with internet
searches and brainstorming with the project team and other members of J.R.M.'s
lab. The final set of questions (and response options) was reviewed and
approved by J.R.M. before we collected or analyzed the text or experimental
data.

We note that estimating the specific ``amount'' of conceptual understanding
that each question ``requires'' to answer is somewhat subjective, and might
even come down to the ``strategy'' a given participant uses to answer the
question at that particular moment. The full set of questions and answer
choices may be found in Supplementary Table~\questions.

>>>>

We then hand-created 39 multiple-choice questions: 15 about the conceptual
content of \textit{Four Fundamental Forces} (i.e., Lecture~1), 15 about the
conceptual content of \textit{Birth of Stars} (i.e., Lecture~2), and 9
questions that tested for general conceptual knowledge about basic physics
(covering material that was not presented in either video). To help broaden the
set of lecture-specific questions, our team worked through each lecture in
small segments to identify what each segment was ``about'' conceptually, and
then write a question about that concept. The general physics questions were
drawn our team's prior coursework and areas of interest, along with internet
searches and brainstorming with the project team and other members of J.R.M.'s
lab. Although we attempted to design the questions to test ``conceptual
knowledge,'' we note that estimating the specific ``amount'' of conceptual
understanding that each question ``requires'' to answer is somewhat subjective,
and might even come down to the ``strategy'' a given participant uses to answer
the question at that particular moment. The full set of questions and answer
choices may be found in Supplementary Table~\questions.  The final set of
questions (and response options) was reviewed and approved by J.R.M. before we
collected or analyzed the text or experimental data.
